Title Goes Here

### 2020-05-05 analysis/paper/paper.Rmd
read in gender data
editing text

---
title: "Title Goes Here"
author:
  - Yichun Chen:
      email: yichun33@uw.edu
      institute: [UofO]
      correspondence: true
  - Ben Marwick:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

# Results
```{r}
number_of_papers_saa_2018 <-  ...
```

- some basic details ( 1 para)
-- number of papers that are in our sample for each conference
-- number of men and women first-named presented, state the gender ratio 
-- number of people that we could not assign a gender to

The number of ... `r number_of_papers_saa_2018` ...

- the main details
-- number of topics that are optimum for each conf (1 para)
-- variance of topics with gender for each conf (1 para)

@@

@@

```{r}
# get plots

@@

SAA18_stm_plot$plot
ggsave(here::here("analysis/figures/SAA18_stm_plot.png"), height = 7, width = 6)

@@

@@

EAA18_stm_plot$plot
ggsave(here::here("analysis/figures/EAA18_stm_plot.png"), height = 7, width = 6)
```

>>>>

---
title: "Title Goes Here"
author:
  - Yichun Chen:
      email: yichun33@uw.edu
      institute: [UofO]
      correspondence: true
  - Ben Marwick:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

# Results

@@

SAA18_gm <- readr::read_rds(here::here("analysis/data/derived-data/SAA18_gender_model.rds")) 
EAA18_gm <- readr::read_rds(here::here("analysis/data/derived-data/EAA18_gender_model.rds"))
CAA18_gm <- readr::read_rds(here::here("analysis/data/derived-data/CAA18_gender_model.rds"))

@@

```{r}
# get plots
library(tidyverse)

@@

SAA18_stm_plot$plot
ggplot2::ggsave(here::here("analysis/figures/SAA18_stm_plot.png"), 
       height = 7, 
       width = 6)

SAA_stm_topic_number <-
  SAA18_stm_plot$model$settings$dim$K
SAA_stm_topic_number_significant_covary <- 
  nrow(layer_data(SAA18_stm_plot$plot, 3))

@@

CAA_stm_topic_number <-
  CAA18_stm_plot$model$settings$dim$K
CAA_stm_topic_number_significant_covary <- 
  nrow(layer_data(CAA18_stm_plot$plot, 3))

@@

EAA18_stm_plot$plot
ggsave(here::here("analysis/figures/EAA18_stm_plot.png"), height = 7, width = 6)

EAA_stm_topic_number <-
  EAA18_stm_plot$model$settings$dim$K
EAA_stm_topic_number_significant_covary <- 
  nrow(layer_data(EAA18_stm_plot$plot, 3))
```

```{r, eval=TRUE}
SAA18_gender <-
  readRDS(here::here("analysis/data/derived-data/SAA18_gender_model.rds"))
EAA18_gender <-
  readRDS(here::here("analysis/data/derived-data/EAA18_gender_model.rds"))
CAA18_gender <-
  readRDS(here::here("analysis/data/derived-data/CAA18_gender_model.rds"))

count_gendered_SAA18 <- nrow(SAA18_gender)
perc_gendered_SAA18 <- round(nrow(SAA18_gender) / SAA18_row, 2) * 100
female_count_SAA18 <- 
  length(which(SAA18_gender$gender == "female"))
male_count_SAA18 <- 
  length(which(SAA18_gender$gender == "male"))
female_to_male_SAA18 <- 
  round(female_count_SAA18 / male_count_SAA18,1)
missing_gender_SAA18 <- 
  SAA18_row - (female_count_SAA18 + male_count_SAA18)

count_gendered_EAA18 <- nrow(EAA18_gender)
perc_gendered_EAA18 <- round(nrow(EAA18_gender) / EAA18_row, 2) * 100
female_count_EAA18 <- 
  length(which(EAA18_gender$gender == "female"))
male_count_EAA18 <- 
  length(which(EAA18_gender$gender == "male"))
female_to_male_EAA18 <- 
  round(female_count_EAA18 / male_count_EAA18, 1)
missing_gender_EAA18 <-
  EAA18_row - (female_count_EAA18 + male_count_EAA18)

count_gendered_CAA18 <- nrow(CAA18_gender)
perc_gendered_CAA18 <- round(nrow(CAA18_gender) / CAA18_row, 2) * 100
female_count_CAA18 <- 
  length(which(CAA18_gender$gender == "female"))
male_count_CAA18 <- 
  length(which(CAA18_gender$gender == "male"))
female_to_male_CAA18 <- 
  round(female_count_CAA18 / male_count_CAA18, 1)
missing_gender_CAA18 <-
  CAA18_row - (female_count_CAA18 + male_count_CAA18)
```

In the SAA data we found at total of `r SAA18_row` presentations. Of these we could identify the first-named author of `r count_gendered_SAA18` (`r perc_gendered_SAA18`%) presentations as either men (n=`r male_count_SAA18`) or women (n=`r female_count_SAA18`). For the CAA meeting we have `r CAA18_row` presentations, and `r count_gendered_CAA18` (`r perc_gendered_CAA18`%) first-named authors could be classified as either men (n=`r male_count_CAA18`) or women (n=`r female_count_CAA18`). For the EAA data we have `r EAA18_row` presentations, and `r count_gendered_EAA18` (`r perc_gendered_EAA18`%) where the first author could be classified as either a man (n=`r male_count_EAA18`) or woman (n=`r female_count_EAA18`). This results in similar women-to-men ratios for the SAA (`r female_to_male_SAA18`) and EAA (`r female_to_male_EAA18`), but much lower for the CAA (`r female_to_male_CAA18`).

In the SAA presentations we identified the optimum number of topics as `r SAA_stm_topic_number`, with `r SAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. One of the main difference that we can see between the topics of the genders are the locations that the presenters are interested in, it seems like that females are more likely to have a topic at a specific region such as mesoamerica, arizona and national parks, while males are more likely to have a topic that are in the western regions.

For EAA we have generated a total of `r EAA_stm_topic_number` topics, with `r EAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. Next, let's take a look at EAA's difference between females and males. Although both red-marked topics include topics with "mediterranean", it is important to distinguish that females seems to be focusing on western mediterranean while males seems to be focusing on northern mediterranean. Another main difference that we have noticed is that males tends to have topics that are related to architect, while the topic regarding research methods using isotopes seems to be more popular for females.

For CAA we hve generated a total of `r CAA_stm_topic_number`, with `r CAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter.. Lastly, in CAA's stm topic plot we can see a clearer pattern from the topics marked in red. For females from CAA, we see that topics that are associated with Geographic Information System (GIS) are more likely to be a topic for female presenters. Another female-associated topics from the CAA topic plot is topics that includes the word women, excav and inform. As for males from CAA, there doesn't seem to have a specific word that is more associated with males besides the word enviorn.
